Constraint Programming - Inside Gecode

### 2014-05-08 paper.tex
moved the branching strategies out of the part about search algorithms

	In the following part I will discuss branching strategies, the Depth-first search, the Branch-and-bound search, the Limited Discrepancy search as candidate for an improved backjumping-strategy, backjumping strategies in general and restart strategies.

	\subsubsection{Branching Strategies}
	If at one node it is not possible to empty one variable domain or to reduce all variable domains to the size of one it is necessary to make a decision: How should the next subtree be constructed? The question is answered by the selected branching strategy. No matter which one is selected, they all have in common that they create additional, temporary constraints, which are only applied to the specific subtrees. This process is called \emph{posting} a constraint on a branch.

@@

>>>>

		\subsection{Branching Strategies}
	If at one node it is not possible to empty one variable domain or to reduce all variable domains to the size of one it is necessary to make a decision: How should the next subtree be constructed? The question is answered by the selected branching strategy. No matter which one is selected, they all have in common that they create additional, temporary constraints, which are only applied to the specific subtrees. This process is called \emph{posting} a constraint on a branch.

@@

	In the following part I will discuss the Depth-first search, the Branch-and-bound search, the Limited Discrepancy search as candidate for an improved backjumping-strategy, backjumping strategies in general and restart strategies.
